Event organizers provide scenarios, which may be either player-vs-GM or player-vs-player.
These scenarios award C-bills through completing objectives and receiving base pay.
The C-bills awarded in a scenario will tend to follow these guidelines:

\begin{itemize}

\item {\bfseries Base Pay}: Each force receives a base payment of 500,000 C-bills.
This C-bill payment represents the baseline cost of a mercenary contract or supplies sent by a faction.

\item {\bfseries Objectives}: Forces earn C-bills for completing primary and secondary objectives.
This C-bill payment represents bonus pay in a mercenary contract and the value of resources or technology acquired by completing mission objectives.

\begin{itemize}

\item Each primary objective is worth no more than 2,000,000 C-bills and is awarded to every player on a side.

\item Each secondary objective is worth no more than 500,000 C-bills and is awarded to each player individually.

\end{itemize}

\end{itemize}

A scenario will have multiple primary and secondary objectives, with each player having the opportunity to earn approximately 5,000,000 C-bills from objectives.

A full list of primary and secondary objectives for each scenario is provided by the event organizers.
This list may change during each scenario as new objectives are revealed.
A sample list of secondary objectives is provided here:

\begin{enumerate}

\item Cripple or \emph{destroy} a 'Mech.

\item Cripple or \emph{destroy} a ProtoMech.

\item Cripple or \emph{destroy} a Combat Vehicle.

\item Cause critical or motive damage on a VTOL unit.

\item Kill at least half of the troops in an infantry unit.

\item Swarm a 'Mech or Combat Vehicle with an infantry unit.

\item Successfully complete a Death from Above attack.

\item Damage an internal section of an opponent's highest BV unit.

\item Capture a vehicle crew or 'Mech pilot.

\end{enumerate}
