In order to use a scenario with \emph{BattleTech: Outworlds Wastes}, force restrictions and allocation of payments should be identified.

Scenario forces should generally match the units available to commanders in the \hyperref[subsec:force_construction]{Force Construction} rules.
For example, a scenario that relies upon a squadron of aerospace fighters would require additional modifications as a commander's DropShip typically has a maximum of two aerospace bays.

Rewards should generally match the guidelines found in the \hyperref[subsec:scenario_scoring]{Scenario Scoring} rules.
For scenarios with victory points, Supply Points, Warchest Points, or other metrics of gradated success between commanders, award the primary objective payment based upon the level of success of each side.
For example, if one side earned 8 victory points and the other side earned 13 victory points out of a total of 25 possible victory points, then award 2,240,000 C-bills to the first side and 3,640,000 C-bills to the second side.

If the scenario has a secondary objective that each side can achieve without preventing the other side from achieving the objective, then award this objective 3,000,000 C-bills.
This payment maybe partially awarded if it is possible to achieve different levels of success for the secondary objective.
If the scenario does not have a secondary objective, then select a secondary objective for the scenario.

League organizers may make adjustments to these guidelines as desired.
