Commanders start with 3,000 BV to acquire initial units for their force.
BV costs for all units are listed in the \href{http://www.masterunitlist.info}{Master Unit List} or \href{https://megamek.org}{MegaMekLab}.
Force construction must follow these rules:

\begin{itemize}

\item Commanders have a modified Leopard class dropship with 4 bays.
Your entire force must fit onto your dropship.

\item Commanders should select units from their faction on the \href{http://www.masterunitlist.info/}{Master Unit List} for the era chosen by event organizers.
Forces can include units with introductory, standard, and advanced technology.
Experimental and unique units are not permitted.

\item Each force must have at least one 'Mech.

\item Each force must have at least one infantry or Battle Armor unit.

\item Each force must have one unit capable of carrying the infantry/Battle Armor unit.
An OmniMech can carry Battle Armor with battle claws.
Mechanized infantry units include vehicles to carry themselves.

\item Forces cannot contain aerospace or off-map battlefield support units.
However, forces can contain any on-map support units, to include on-map artillery.

\item The BV costs of a unit includes all adjustments, to include skill levels, C\textsuperscript{3}, and TAG.
Skill levels should generally be close to the average skill levels given on page 40 of \emph{BattleTech: Total Warfare}.
The skill levels for a unit may be no better than Gunnery 3/Piloting 4.
ProtoMechs and mechanized infantry always have Piloting/Anti-'Mech 5, because these skills are not used for these units.

\end{itemize}

Commanders must bring the rulebooks for any special equipment for units in their force not found in \emph{BattleTech: Total Warfare}.
Unit record sheets can be generated using \href{https://megamek.org}{MegaMekLab} or similar tools.

BV costs sometimes do not mach between the \href{http://www.masterunitlist.info}{Master Unit List} and \href{https://megamek.org}{MegaMekLab}, especially for infantry units, due differences in the official rules.
Commanders must use the same source for all BV costs.
All record sheets must agree with the BV costs from this source.

Commanders may use a new force for each scenario.
Alternatively, commanders may maintain and improve their force between scenarios with the \ifthenelse{\equal{\outworldsMode}{mode-pdf-event}}{Force Maintenance rules, page \pageref{subsec:event_force_maintenance}}{\hyperref[subsec:event_force_maintenance]{Force Maintenance} rules}.
An improved force may exceed the 3,000 BV limit but must otherwise follow the limitations given above.
However, a maximum of 5,000 BV can be fielded by a commander in any scenario.

Two sample initial forces are provided; the first force is an ilClan era mercenary unit and the second force is an ilClan era Raven Alliance detachment.
Pilot names are encouraged, as one of the goals is to develop the personalized lore for your force.

\begin{table}[!h]
\ifthenelse{\equal{\outworldsMode}{mode-pdf}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{| m{2em} m{12em} m{8em} R{4.6em} R{4.6em} R{3.5em} R{3.8em} |}
\hline
\rowcolor{black!30}  \bfseries{Bay} & \bfseries{Unit} & \bfseries{Pilot} & \bfseries{Gunnery} & \bfseries{Piloting} & \bfseries{BV} & \bfseries{Adj BV} \\
\hline
1   & Archer ARC-7S         & 'Meg' Courant    & 3       & 4         & 1,658 & 2,189 \\
2   & Calvary Attack (BA)   & 'Bugs' Schwann   & 3       & 5         &   604 &   725 \\
3   & Jump Platoon (Rifle)  & Ralph Nosske     & 3       & 4         &    79 &    82 \\
\hline
    & Total BV              &                  &         &           &       & 2,996 \\
\bottomrule
\end{tabular}
\caption*{ilClan Era Mercenary Force - Meg's Magpies}
\end{table}

\begin{table}[!h]
\ifthenelse{\equal{\outworldsMode}{mode-pdf}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{| m{2em} m{12em} m{8em} R{4.6em} R{4.6em} R{3.5em} R{3.8em} |}
\hline
\rowcolor{black!30}  \bfseries{Bay} & \bfseries{Unit} & \bfseries{Pilot} & \bfseries{Gunnery} & \bfseries{Piloting} & \bfseries{BV} & \bfseries{Adj BV} \\
\hline
1   & Carrion Crow C        & Sarah Magnus    & 3       & 4         & 1,826 & 2,410 \\
2   & Elemental BA [Laser]  & Harry           & 3       & 4         &   447 &   590 \\
\hline
    & Total BV              &                 &         &           &       & 3,000 \\
\bottomrule
\end{tabular}
\caption*{ilClan Era Raven Alliance Force - Raven Expeditionary Cluster}
\end{table}
