\begin{enumerate}

\item {\bfseries Reconnaissance}: The map contains 15 buildings, 7 of which contain hidden objectives.
Place the buildings randomly or each side takes turns placing the buildings.
The defender secretly rolls to determine which buildings hold the objectives.
Attacking units may search buildings during the End Phase if they are in the target hex (in base to base contact, Alpha Strike) and no enemy units are in the target hex.
The search is successful on a 2D6 roll of 7+ for 'Mechs and ground combat vehicles or 5+ for infantry.
An attacking unit with an active probe may instead search 1 building within range of its active probe on a 2D6 roll of 6+.
The attacker earns 1,000,000 C-bills for each objective they find and the defender earns 1,000,000 C-bills for each objective remaining hidden.

\item {\bfseries Supply Raid}: 3-7 supply depots are on the map, near the center.
Each supply depot has 1-3 loads of supplies.
Any unit with hands or cargo capacity can load supplies from the depot if they are in the same hex as a supply depot (in base to base contact, Alpha Strike) during the End Phase.
A 'Mech with hand actuators must declare which hand is holding the supplies.
For units with cargo capacity, a friendly infantry unit must load or unload the supplies during the End Phase.
Units involved in loading or unloading supplies cannot make weapon or physical attacks during that turn.
A 'Mech carrying supplies can't fire arm weapons (BattleTech) or does -2 damage (Alpha Strike).
The supplies have negligible weight.
There is no movement penalty and jumping units may still jump while carrying supplies.
Carrying supplies does not decrease the infantry space in a combat vehicle, but all standard infantry mount and dismount rules still apply.
'Mechs carrying supplies in their hands may drop the supplies at any point during their movement.
The supplies are automatically dropped if the carrying 'Mech falls or goes prone.
Units with cargo capacity must be unloaded by a friendly infantry unit.
Each side cannot retrieve more supplies from the same supply depot until the current supplies from that depot are scored.
A unit carrying supplies earns a portion of 7,000,000 C-bills for bringing the supplies to their home edge based upon the total number of loads of supplies available.

\item {\bfseries Zone Control}: 3, 5, or 7 key points are distributed on the map.
The locations of the key points dramatically changes the gameplay.
The basic configuration is 3 key points along the center of the map and 1 key point halfway between the center and each home edge.
A side controls a key point if only their units are in or adjacent to the key point (within 2", Alpha Strike).
During the End Phase, the side that controls the most key points earns 1,000,000 C-bills.
If each side controls the same number of points and controls at least 1 point, then each side earns 500,000 C-bills for that round.

\item {\bfseries Base Defense}: 7 buildings are on the defenders side of the map.
Each building is medium with a construction factor of 60 (6, Alpha Strike) and 1-3 levels high (1"-3", Alpha Strike), unless the players agree upon a different configuration.
The attacker earns 1,000,000 C-bills for each building destroyed and the defender earns 1,000,000 C-bills for each building remaining.

\item {\bfseries King of the Hill}: A hex in the center of the map contains a building with valuable files.
The building is medium with a construction factor of 60 (6, Alpha Strike), unless the players agree upon a different configuration.
The force earns 1,000,000 C-bills for every turn that they have the only infantry units inside of the building at the end of the turn.
Commanders may add additional bunkers to the center of the map and split the 1,000,000 C-bills between the number of bunkers.

\item {\bfseries Assassination}: A VIP needs to be escorted across the battlefield.
The defender selects a medium or heavy 'Mech from the Periphery General or Pirates list.
The VIP is a Gunnery 5/ Piloting 4 (Skill 4, Alpha Strike) pilot and half of the adjusted BV/PV of the 'Mech counts against the defender's BV/PV limit.
The VIP's 'Mech must cross the map from the defender's home edge to the attacker's home edge.
The attacker earns 7,000,000 C-bills if this 'Mech is destroyed or 3,500,000 C-bills if this 'Mech receives crippling damage.
The defender 7,000,000 C-bills if this 'Mech does not receive crippling damage or 3,500,000 C-bills if this 'Mech is crippled but not destroyed.
The turn limit for this scenario is based upon the terrain and movement profile of the VIP's 'Mech.

\item {\bfseries Extraction}: Extract 1-3 hidden infantry teams.
For each hidden unit, the attackers select a hex within 4 rows (8", Alpha Strike) of the defenders home edge and more than 4 hexes (8", Alpha Strike) away from the other edges of the map.
A unit with at least 1 ton of cargo capacity can pick up the target by being in the same hex as a target during the End Phase.
The target is not destroyed if the carrying unit is destroyed.
A unit earns a portion of 7,000,000 C-bills by exiting their home edge while carrying a target.

\item {\bfseries Recovery}: 4-6 disabled 'Mechs are equally spaced along the map diagonal.
A unit of equal or higher weight class can drag a target 'Mech.
A friendly unit must be in the same hex (in base to base contact, Alpha Strike) as the target 'Mech during the End Phase to start dragging it.
Units without hand actuators must use 1 turn securing the target 'Mech.
The dragging unit has a 1/2 reduction in their walking MP and cannot jump.
A target 'Mech cannot fire weapons in one arm (BattleTech) or does -1 damage (Alpha Strike).
A unit earns a proportion of 7,000,000 C-bills for each 'Mech returned to their home map edge.

\end{enumerate}
