By default, \emph{BattleTech: Outworlds Wastes} uses full rules for aerospace and artillery units from \emph{BattleTech: Total Warfare} and \emph{Alpha Strike: Commander's Edition}.
League organizers may allow Battlefield Support rules ( p. 75, \emph{BMM}) to provide simplified aerospace and artillery support for BattleTech and off-board artillery rules for Alpha Strike (see p. 151, \emph{AS: CE}).

Each side for a scenario must agree to use Battlefield Support or off-board artillery rules.
When using Battlefield Support rules in \emph{BattleTech} scenarios, each side receives the same number of Battlefield Support Points (BSPs) and may use them at any point during the scenario.
A typical 6,000 BV 1v1 game would have 12 BSPs per side while a typical 10,000 BV 2v2 game would have 20 BSPs.

The following additional rules apply when using Battlefield Support or off-board artillery.

\begin{itemize}

\item The commander's force must have a unit capable of offering the support.

\begin{table}[!h]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{18em} m{20em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Support Type} & \bfseries{Required Unit} \\
\Hline{1pt}
Offensive Aerospace Support (BSP)   & Attack or fire-support aerospace unit    \\
Defensive Aerospace Support (BSP)   & Dogfighter or interceptor aerospace unit \\
Artillery Support (BSP)             & Corresponding artillery unit             \\
Counter-Battery Support (BSP)       & Artillery or aerospace unit              \\
Minefield Support (BSP)             & Any unit                                 \\
Off-board Artillery (Alpha Strike)  & Artillery unit                           \\
Counter-Battery Fire (Alpha Strike) & Artillery or aerospace unit              \\
\Hline{1pt}
\end{tabular}
\caption*{Support Unit Requirements}
\end{table}

\item The commander must declare which off-map unit in their force is offering support during the scenario before using the off-map support rules.
The same unit must be used to provide this type of support for the rest of the scenario, unless this unit is destroyed.

\item The first successful use of Defensive Aerospace Support or Counter-Battery Support/Fire damages the attacking unit.
The second successful use destroys the attacking unit.

\end{itemize}

{\bfseries Counter-Battery Support}: Counter-Battery Support is a new form of Battlefield Support.
Counter-Battery Support costs 3 BSPs and can only be used once enemy Artillery Support has been used.
The Target Number for Counter-Battery Support is 7.
Reduce the Target Number by 1 for each use of enemy Artillery Support where a friendly unit had LOS to the point of impact.
Reset the Target Number to 7 if the enemy artillery unit is destroyed by 2 successful Counter-Battery Support attacks.
