\begin{enumerate}

\item {\bfseries Reconnaissance}: The map contains 15 buildings that are at least 1 hex large, 7 of which contain hidden objectives.
These buildings can be distributed randomly or by each player taking turns placing a building.
The defender rolls in secret to determine which buildings hold the hidden objectives.
The attacker earns 1,000,000 C-bills for each hidden objective they find.
The defender earns 1,000,000 C-bills for each hidden objective the attacker does not find.

\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{
\item {\bfseries Supply Raid}: 3-7 supply depots are on the map, near the center.
Each supply depot has 1-3 loads of supplies.
Any unit with hands or cargo capacity can load supplies from the depot if they end their Movement Phase in the same hex.
Standard cargo loading rules apply.
A unit carrying supplies in their hands cannot fire any arm mounted weapons.
A unit carrying supplies earns a portion of 7,000,000 C-bills for bringing the supplies to their home edge.
Each side cannot score from the same supply depot twice until they score from every other supply depot.
}{
% Errata
\item {\bfseries Supply Raid}: 3-7 supply depots are on the map, near the center.
Each supply depot has 1-3 loads of supplies.
Any unit with hands or cargo capacity can load supplies from the depot if they end the Movement Phase in the same hex.
Standard cargo loading rules apply.
A 'Mech carrying supplies can't fire arm weapons (BattleTech) or does -2 damage (Alpha Strike).
A unit carrying supplies earns a portion of 7,000,000 C-bills for bringing the supplies to their home edge.
Each side cannot score from the same supply depot twice until they score from every other supply depot.
}

\item {\bfseries Zone Control}: 3, 5, or 7 key points are distributed on the map.
The locations of the key points dramatically changes the gameplay.
The basic configuration is 3 key points along the center of the map and 1 key point halfway between the center and each home edge.
A side controls a key point if only their units are in or adjacent to the key point.
During the End Phase, the side that controls the most key points earns 1,000,000 C-bills.
If each side controls the same number of points and controls at least 1 point, then each side earns 500,000 C-bills for that round.

\item {\bfseries Base Defense}: 7 buildings are on the defenders side of the map.
Each building is medium with a construction factor of 60 and 1-3 levels high, unless the players agree upon a different configuration.
The attacker earns 1,000,000 C-bills for each building destroyed and the defender earns 1,000,000 C-bills for each building remaining.

\item {\bfseries King of the Hill}: A hex in the center of the map contains a building with valuable files.
The building is medium with a construction factor of 60, unless the players agree upon a different configuration.
The force earns 1,000,000 C-bills for every turn that they have the only infantry/Battle Armor units inside of the building at the end of the turn.

\item {\bfseries Assassination}: A local militia commander needs to be escorted across the battlefield.
The defender selects a medium or heavy 'Mech from the Periphery General or Pirates list.
The commander is a Gunnery 5/ Piloting 4 pilot and half of the adjusted BV of the 'Mech counts against the defender's BV limit.
The militia commander pilots this 'Mech and must transit the map from the defender's home edge to the attacker's home edge.
The attacker earns 7,000,000 C-bills if the commander's 'Mech is destroyed or 3,500,000 C-bills if the commander's 'Mech receives crippling damage.
The defender 7,000,000 C-bills if the commander's 'Mech does not receive crippling damage  or 3,500,000 C-bills if the commander's 'Mech is crippled but not destroyed.

\item {\bfseries Extraction}: Extract 1-3 hidden infantry teams.
For each hidden unit, the attackers select a hex within 4 rows of the defenders home edge and more than 4 hexes away from the other edges of the map.
A unit with at least 1 ton of cargo capacity can pick up the target by being in the same hex as a target during the End Phase.
The target is not destroyed if the carrying unit is destroyed.
A unit earns a portion of 7,000,000 C-bills by exiting their home edge while carrying a target.

\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{
\item {\bfseries Recovery}: 4-6 disabled 'Mechs are equally spaced along the map diagonal.
A unit of equal or higher weight class can drag a disabled 'Mech.
To start dragging a disabled 'Mech, a friendly unit must end the turn in the same hex as the disabled 'Mech.
Units without hand actuators must use 1 turn securing the disabled 'Mech.
The dragging unit has a 1/2 reduction in their walking MP and cannot jump.
A dragging 'Mech cannot fire any weapons on the arm it uses for dragging.
A unit earns a proportion of 7,000,000 C-bills for dragging a disabled 'Mech to its home map edge.
}{
\item {\bfseries Recovery}: 4-6 disabled 'Mechs are equally spaced along the map diagonal.
A unit of equal or higher weight class can drag a target 'Mech.
A friendly unit must be in the same hex as the target 'Mech during the End Phase to start dragging it.
Units without hand actuators must use 1 turn securing the target 'Mech.
The dragging unit has a 1/2 reduction in their walking MP and cannot jump.
A target 'Mech cannot fire weapons in one arm (BattleTech) or does -1 damage (Alpha Strike).
A unit earns a proportion of 7,000,000 C-bills for each 'Mech returned to their home map edge.
}

\end{enumerate}
