Scenarios award C-bills through completing objectives or receiving base pay.
The C-bills awarded in a scenario will tend to follow these guidelines:

\begin{description}

\item {\bfseries Objectives}: Forces earn C-bills for completing primary and secondary objectives.
This C-bill payment represents bonus pay in a mercenary contract and the value of resources or technology acquired by completing mission objectives.
Objective payments should be proportionally adjusted if the BV limit for the scenario differs from the typical limit.

\begin{itemize}

\item The primary objective is typically worth 7,000,000 C-bills and is split between the two sides based upon the portion of the primary objective completed.

\item The secondary objectives are typically worth 3,000,000 C-bills and each objective is awarded to each side separately.

\end{itemize}

\item {\bfseries Base Pay}: If the force did not complete any objectives, then the force earns 2,000 C-bills for every 10 BV for the scenario, with a minimum of 600,000 C-bills.
For example, a 6,000 BV vs 6,000 BV scenario will have a base payout of 1,200,000 C-bills.
This C-bill payment represents the baseline cost of a mercenary contract or supplies sent by a faction.

\end{description}

Scenarios do not typically require a Game Master to run additional third party forces.
If there are third party forces that require an additional person, this person may receive C-bills for one of their Outworlds Wastes forces.
This C-bill payment should not exceed the maximum C-bill payment for the scenario, and it should be close to the average of the payments that the players in the scenario received.
The exact conditions for the payout should be agreed upon before the scenario starts.
