\emph{BattleTech: Chaos Campaign} is a free PDF with campaign rules that have lower complexity than \emph{BattleTech: Campaign Operations}.
The Chaos Campaign rules are used for campaigns in \emph{BattleTech: Chaos Campaign: Succession Wars} as well as \emph{BattleTech: Spotlight On} and \emph{BattleTech: Turning Points} publications and \emph{Shrapnel}, the BattleTech magazine.

Campaigns written with Chaos Campaign tracks can be converted to \emph{BattleTech: Outworlds Wastes}:

\begin{enumerate}

\item Pick the BV/PV limit for the track with highest Warchest Points (WP) track cost.

\item Determine the BV/PV limits for each track in the campaign.
These limits are given by multiplying the maximum BV/PV limit by the ratio between the current track's WP cost and the highest WP cost for a track.
For example, in a campaign with a max WP track cost of 300 WP commanders might agree upon setting the BV limit for that track at 8,000 BV.
A track with a 100 WP cost would then have a 2,667 BV limit.
If one side may only field a smaller portion of their force, set their BV limit proportional to the full limit.
For example, if the defender may only field 75\% of their force while the attacker may field up to 100\% of their force in a track with a 4,000 BV limit, then the defender may only use 3,000 BV.

\item Compute the WP to C-bills conversion: (7,000,000 C-bills) $\div$ (6,000 BV/150 PV) $\times$ (BV/PV limit) $\div$ (Max WP track cost), rounding up.
For example, for a campaign with a max WP track cost of 300 WP where the largest track will be played with 8,000 BV, the WP to C-bills conversion is 31,112 C-bills per WP.
\item Determine the C-bill payouts for objectives in the campaign.
In the example above, objectives worth 100 WP would earn 3,111,100 C-bills and 200 WP objectives earn 6,222,200 C-bills.

\item Secondary objectives may be added to individual tracks, such as those given in the Casual Scenarios section.
The maximum C-bill payment should remain close to 10,000,000 C-bills for a 6,000 BV/150 PV track, or appropriately scaled for a track with different BV/PV limits.
However, some tracks intentionally pay out significantly more or less WP than their WP cost.

\item The optional Warchest costs can be added to any scenario at no C-bill cost, as long as these options do not grant additional forces or Battlefield Support to either side.
For example, an option that adds weather conditions may be selected while an option that adds a minefield may not.

\item Additional rules or setup are included in some tracks.
These additional rules do not always fit well with \emph{BattleTech: Outworlds Wastes} and Commanders will need to decide how to best meet the spirit of these rules.

\item All tracks must be converted and agreed upon, before commanders begin the campaign.

\end{enumerate}
