\section{Version 2.0}

This errata applies to version 2.0 of the BattleTech: Outworlds Wastes rules.

\subsection{Force Maintenance and Improvements}

Update the \emph{repair} rule to make motive system damage free to repair.

\begin{description}

\item {\bfseries Repair}: Pay 25\% of the C-bill cost, rounded up, to repair all internal damage and critical components for a unit that has not been \emph{destroyed}.
If the pilot/crew was killed, the repair cost includes a 5/6 pilot or crew that may be \emph{trained}.
Armor and motive systems are repaired for free.
For Omni units, the repair cost is based upon the fielded variant.

\end{description}

\subsection{Advanced Force Maintenance and Improvements}

\subsubsection{Contracts}

Add the following new optional rules.

\begin{description}

\item {\bfseries Contracts}: Negotiate the terms of your employment to receive lower objective payments in exchange for reduced repair costs.
All contract terms start at level 1.
Commanders may raise the level of contract terms in pairs.
For example, to go from level 1 in Repair Costs to level 2, a commander must also go to level 2 in either Objective Pay or Salvage.

Multiply the \emph{repair} and \emph{replace} costs by the percentage given by the Repair Costs level.
Multiply the C-bills earned from objectives by the percentage given by Objective Pay level.
Multiply the C-bills earned from salvage by the percentage given by the Salvage level.
Also, commanders may only add a portion of the enemy units destroyed to their force, given by the total number of enemy units destroyed multiplied by the percentage given by the Salvage level, rounded up.

\begin{table}[!h]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\begin{tabular}{!{\Vline{1pt}} m{5em} | m{8em} | m{8em} | m{8em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30} \bfseries{Level} & \bfseries{Objective Pay} & \bfseries{Salvage} & \bfseries{Repair Costs} \\
\Hline{1pt}
1 & 100\% & 100\% & 100\% \\
2 &  75\% &  65\% &  80\% \\
3 &  50\% &  35\% &  60\% \\
4 &  25\% &   0\% &  40\% \\
5 &   0\% &   -   &  20\% \\
\Hline{1pt}
\end{tabular}
\caption*{Contract Terms}
\end{table}

This optional rule cannot be used when using \emph{BattleTech: Chaos Campaign} rules from the \emph{Hot Spots: Hinterlands} sourcebook or the \emph{BattleTech: Mercenaries} box set.

\item {\bfseries Timetables}: Maintenance activities take time to complete.
\emph{Repair} takes 1 scenario to complete.
\emph{Replace} and \emph{Refit} take two scenarios to complete.
Commanders may pay double the C-bill cost to reduce this time by 1 scenario.
Also, pilots only heal one point of damage between scenarios.

\end{description}

\subsubsection{Dropship Customization}

Double the percentage benefits and detriments for all improvement levels.
For example, Level 1 of Machine Shop now grants a 10\% decrease in salvage costs instead of a 5\% decrease.
