\section{Version 3.1}

This errata applies to version 3.1 of the BattleTech: Outworlds Wastes rules.

\subsection{Advanced Force Maintenance}

\subsubsection{Slim Resources}

Add the following new optional rule.

\begin{description}

\item {\bfseries Slim Resources}: League organizers may restrict \emph{refit} and \emph{purchase} options to represent limited resources in a campaign.

\end{description}

\subsubsection{Full DropShip Customization}

Add the following new optional rule.

\begin{description}

\item {\bfseries Full DropShip Customization}: Commanders may create a fully customized DropShip from a civilian model.
Commanders are encouraged to name their DropShip before using this rule.
Commanders should keep track of their DropShip customizations, as shown on the \ifthenelse{\equal{\outworldsMode}{mode-web}}{sample \hyperref[sec:sample_full_dropship]{Full DropShip tracking}}{\emph{Sample Full DropShip Customization Tracking}}.

Commanders start with a civilian DropShip and note the maximum cargo bay tonnage.
For example, the Danais, a commonly modified civilian DropShip, has a maximum cargo bay tonnage of 1,693 tons.
Commanders may purchase bays to replace the cargo bay tonnage, as long as the maximum cargo bay tonnage is not exceeded.

The table below details bay tonnage and C-bill costs.
The C-bill costs include the basic cost of the bay as well as the labor required for the modifications.

\begin{table}[!h]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{L}[1]{>{\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\vrule width 1pt} m{8em} L{12em} R{5em} !{\vrule width 1pt}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Bay Type} & \bfseries{Tons} & \bfseries{Cost} \\
\Hline{1pt}
'Mech          & 150 tons                 & 520,000 \\
Combat Vehicle & 100 tons                 & 510,000 \\
Aerospace      & 150 tons                 & 520,000 \\
ProtoMech      &  50 tons                 & 510,000 \\
Infantry       &  15 tons or unit tonnage & 515,000 \\
\Hline{1pt}
\end{tabular}
\caption*{DropShip Bay Customization Costs}
\end{table}

Commanders may also add additional equipment to their dropships to gain the \ifthenelse{\equal{\outworldsMode}{mode-web}}{\hyperref[subsubsec:dropship_customization]{\emph{DropShip Customization}} benefits}{\emph{DropShip Customization} benefits}. 
Commanders can customize their DropShips in the following categories:

\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\begin{multicols}{2}}{}

\begin{itemize}

\item 'Mech Maintenance

\item Ground Combat Vehicle Maintenance

\item VTOL Combat Vehicle Maintenance

\item Aerospace Unit Maintenance

\item ProtoMech Maintenance

\item Machine Shop

\item Medical Bay

\item Infantry Quarters

\item Simulators

\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\vfill\mbox{}}{}

\end{itemize}

\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\end{multicols}}{}

The table below details bay tonnage and C-bill costs for the customization levels.

\begin{table}[!h]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{L}[1]{>{\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\vrule width 1pt} m{8em} L{12em} R{5em} !{\vrule width 1pt}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Bay Type} & \bfseries{Tons} & \bfseries{Cost} \\
\Hline{1pt}
Level 1 &  50 tons &   500,000 \\
Level 2 & 100 tons & 1,000,000 \\
Level 3 & 200 tons & 2,000,000 \\
\Hline{1pt}
\end{tabular}
\caption*{DropShip Facility Customization Costs}
\end{table}

\end{description}
