By default, \emph{BattleTech: Outworlds Wastes} assumes commanders are using the full rules for combined arms from \emph{BattleTech: Total Warfare} and \emph{Alpha Strike: Commander's Edition}.
Commanders may use Battlefield Support: Strikes rules (p. 75, \emph{BMM}  and p.55, \emph{AS: CE}) to provide simplified aerospace and artillery support and off-board artillery rules for Alpha Strike (see p. 151, \emph{AS: CE}).

Each side for a scenario must agree to use Battlefield Support: Strikes or off-board artillery rules.
When using Battlefield Support: Strikes rules, each side receives the same number of Battlefield Support Points (BSP).
Consult the Battlefield Support rules in \emph{BattleTech: Mercenaries} box set or \emph{Alpha Strike: Commander's Edition}, as appropriate, to help determine the number of BSP and the cost of each support type.
Each side may also agree to use any unused BV from force selection to purchase additional BSP, where 1 BSP costs 20 BV.

The following additional rules apply when using Battlefield Support: Strikes or off-board artillery.

\begin{itemize}

\item The commander's force must have a unit capable of offering the support.

\begin{table}[!h]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{18em} m{20em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Support Type} & \bfseries{Required Unit}   \\
\Hline{1pt}
Offensive Aerospace Support    & Attack or fire-support aerospace unit    \\
Defensive Aerospace Support    & Dogfighter or interceptor aerospace unit \\
Artillery Support              & Corresponding artillery unit             \\
Counter-Battery Support        & Artillery or aerospace unit              \\
Minefield Support              & Any unit                                 \\
\Hline{1pt}
\end{tabular}
\caption*{Support Unit Requirements}
\end{table}

\item The commander must declare which off-map unit in their force is offering support during the scenario before using the off-map support rules.
The same unit must be used to provide this type of support for the rest of the scenario, unless this unit is destroyed.

\item Commanders declare what Battlefield Support: Strikes they are using this turn at the start of the Weapon Attack Phase while declaring attacks.

\item The first successful use of Defensive Aerospace Support or Counter-Battery Support/Fire damages the attacking unit.
The second successful use destroys the attacking unit.

\end{itemize}

Counter-Battery Support is a new form of Battlefield Support for BattleTech that mirrors the Counter-Battery Fire rule from Alpha Strike.

{\bfseries Counter-Battery Support}:
Counter-Battery Support costs 14 BSP and can only be used once enemy Artillery Support has been used.
The Target Number for Counter-Battery Support is 7.
Reduce the Target Number by 1 for each use of enemy Artillery Support where a friendly unit had LOS to the point of impact.
Reset the Target Number to 7 if the enemy artillery unit is destroyed by 2 successful Counter-Battery Support attacks.
