Event organizers provide tracks, which may be 1v1, 2v2, or 1v2.
Commanders may use different units for different tracks in a contract.

The standard rules given in the \emph{BattleTech: Mercenaries} box set and the \emph{BattleTech: Hinterlands} sourcebook apply to these tracks, unless the organizers modify these rules.

For 1v1 tracks, commanders may bring 6,000 BV (200 PV) of units to each track, excluding the cost of Skill Advances but including any costs of C\textsuperscript{3} and TAG.
Commanders may convert up to 2,000 BV to 100 BSP and run the non-'Mech units as Battlefield Support: Assets; however, Assets may not score objectives.

For 2v2 tracks, commanders may bring 3,000 BV (85 PV) of 'Mechs to each track, excluding the cost of Skill Advances but including any costs of C\textsuperscript{3} and TAG.
Commanders may bring 1,000 BV (40 PV) of non-'Mech units, plus any unspent BV (PV) from 'Mech units, for a total of 4,000 BV (125 PV).
Commanders may convert up to 1,000 BV to 50 BSP and run the non-'Mech units as Battlefield Support: Assets; however, Assets may not score objectives.

For 1v2 tracks, the commanders working together select their units per the 2v2 limits given above.
The independent commander may bring 8,000 BV (250 PV) of units to each track, excluding the cost of Skill Advances but including any costs of C\textsuperscript{3} and TAG.
The independent commander may convert up to 2,000 BV to 100 BSP and run the non-'Mech units as Battlefield Support: Assets; however, Assets may not score objectives.

Commanders start with 14 SP for Battlefield Support: Strikes, or 28 SP for the independent commander in a 1v2 track.
Any unspent BV may be convert to BSP to use for Strikes, unless prohibited by the event rules.
