Secondary objectives are additional goals added to each track.
Commanders earn 50 SP if their force completes their secondary objective.
In a 1v2 track, the independent commander may have two separate secondary objectives a single secondary objective that they may score twice.

There are three ways to select secondary objectives.
First, a single secondary objective that both sides share could be selected, randomly or by mutual agreement.
Alternatively, each side could randomly roll a secondary objective in secret.
Finally, each player could randomly roll a secondary objective in secret.

The selected secondary objectives must be achievable by the forces selected for the scenario.
If a secondary objective is impossible to accomplish based upon the scenario, map, or enemy force, determine a new secondary objective before play begins.

\begin{enumerate}

  \item Cripple or \emph{destroy} a 'Mech.

  \item Cripple or \emph{destroy} a ProtoMech.

  \item Cripple or \emph{destroy} a Combat Vehicle.

  \item Cause critical or motive damage on a VTOL or aerospace unit.

  \item Kill at least half of the troops (remove all armor, Alpha Strike) in an infantry unit.

  \item Swarm a 'Mech or Combat Vehicle with an infantry unit.

  \item Successfully complete a Death from Above attack.

  \item Damage an internal section of an opponent's highest BV/PV unit.

  \item \emph{Capture} a vehicle crew or 'Mech pilot.

  \item Extract a hidden unit from within 4 hexes (8", Alpha Strike) of the far map edge.

\end{enumerate}
