Commanders start with 3,000 BV to acquire initial units for their force.
BV costs for all units are listed in the \href{http://www.masterunitlist.info}{Master Unit List} or \href{https://megamek.org}{MegaMekLab}.
Force construction must follow these rules:

\begin{itemize}

\item Commanders have a modified Leopard class DropShip that can hold a maximum of 4 units.
Your entire force must fit onto your DropShip.

\item Commanders should select units from one faction on the \href{http://www.masterunitlist.info/}{Master Unit List} for the era chosen by event organizers.
Forces may include units with introductory, standard, and advanced technology.
Custom, experimental, and unique units are not permitted.

\item Each force must have at least one 'Mech.

\item Each force must have at least one Battle Armor unit.
If Battle Armor is not available to the faction in the era, then the force must contain at least one non-mechanized conventional infantry unit.

\item Each force must have one unit capable of carrying the Battle Armor (or infantry) unit.
An OmniMech can carry standard Battle Armor.
BattleMechs can carry Battle Armor equipped with magnetic clamps, but receive a -1 MP/-2 inch reduction to their Walking MP (p. 227, \emph{TW}, p. 39, \emph{AS: CE}).

\item Forces cannot contain aerospace or battlefield support units, including on-map artillery.

\item The BV costs of a unit includes all adjustments, to include skill levels, C\textsuperscript{3}, and TAG.
Skill levels should generally be close to the average skill levels (see p. 40, \emph{TW}).
A unit may be no better than Gunnery 3/Piloting 4 and no worse than Gunnery 5/Piloting 6.
ProtoMechs always have Piloting 5 and infantry units without anti-'Mech equipment have Anti-'Mech 5.

\end{itemize}

Commanders must bring the rulebooks for any special equipment not found in \emph{BattleTech: Total Warfare} or \emph{BattleTech: BattleMech Manual}.
Unit record sheets can be generated using \href{https://megamek.org}{MegaMekLab} or similar tools.

BV costs sometimes do not mach between the \href{http://www.masterunitlist.info}{Master Unit List} and \href{https://megamek.org}{MegaMekLab}, especially for conventional infantry units, due differences in the official rules.
Commanders must use the same source for all BV costs.
All record sheets must agree with the BV costs from this source.

Commanders may maintain and improve their force between scenarios with the \ifthenelse{\equal{\outworldsMode}{mode-pdf-event}}{\emph{Force Maintenance} rules (see p. \pageref{subsec:event_force_maintenance})}{\hyperref[subsec:event_force_maintenance]{Force Maintenance} rules}.
Improved forces cannot exceed 5,000 BV and must follow the other rules above.
See the \ifthenelse{\equal{\outworldsMode}{mode-pdf-event}}{\emph{Sample Scenario Logistics Tracking} (p. \pageref{sec:sample_event_roster})}{sample \hyperref[sec:sample_event_roster]{force tracking} sheet}.
Commanders instead reset their force between scenarios.

Two sample initial forces are provided; the first force is an ilClan era mercenary unit and the second force is an ilClan era Raven Alliance detachment.
Pilot names are encouraged, as one of the goals is to develop the personalized lore for your force.

\begin{table}[!h]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{2em} m{12em} m{8em} R{4.6em} R{4.6em} R{3.5em} R{3.8em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Bay} & \bfseries{Unit} & \bfseries{Pilot} & \bfseries{Gunnery} & \bfseries{Piloting} & \bfseries{BV} & \bfseries{Adj BV} \\
\Hline{1pt}
1   & Archer ARC-7S       & 'Meg' Courant    & 3       & 5         & 1,658 & 1,990 \\
2   & Cavalry Attack (BA) & 'Bugs' Schwann   & 3       & 5         &   604 &   725 \\
3   & IS Standard (Laser) & Ralph Nosske     & 3       & 5         &   231 &   277 \\
\hline
    & Total BV            &                  &         &           &       & 2,992 \\
\Hline{1pt}
\end{tabular}
\caption*{ilClan Era Mercenary Force - Meg's Magpies}
\end{table}

\begin{table}[!h]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{2em} m{12em} m{8em} R{4.6em} R{4.6em} R{3.5em} R{3.8em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Bay} & \bfseries{Unit} & \bfseries{Pilot} & \bfseries{Gunnery} & \bfseries{Piloting} & \bfseries{BV} & \bfseries{Adj BV} \\
\Hline{1pt}
1   & Carrion Crow C        & Sarah Magnus    & 3       & 4         & 1,826 & 2,410 \\
2   & Elemental BA [Laser]  & Harry           & 3       & 4         &   447 &   590 \\
\hline
    & Total BV              &                 &         &           &       & 3,000 \\
\Hline{1pt}
\end{tabular}
\caption*{ilClan Era Raven Alliance Force - Raven Expeditionary Cluster}
\end{table}
