\section{Version 1.1}

This errata applies to version 1.1 of the BattleTech: Outworlds Wastes rules.

\subsection{Casual Scenario Primary Objectives}

The following changes fix Alpha Strike compatibility for Casual Scenarios.
Update the following items on p. 28 of the full rules and p. 9 of the quickstart rules  as follows:

\begin{enumerate}

\item {\bfseries Reconnaissance}: The map contains 15 buildings, 7 of which contain hidden objectives.
Place the buildings randomly or in turn.
The defender secretly rolls to determine which buildings hold the objectives.
Attacking units may search buildings during the End Phase if they are in the target hex with no enemy units.
An attacking unit with an active probe may instead search 1 building within range of its active probe on a roll of 6+.
The attacker earns 1,000,000 C-bills for each objective they find and the defender earns 1,000,000 C-bills for each objective remaining hidden.

\setcounter{enumi}{3}
\item {\bfseries Base Defense}: 7 buildings are on the defenders side of the map.
Each building is medium with a construction factor of 60 (6 for Alpha Strike) and 1-3 levels high, unless the players agree upon a different configuration.
The attacker earns 1,000,000 C-bills for each building destroyed and the defender earns 1,000,000 C-bills for each building remaining.

\item {\bfseries King of the Hill}: A hex in the center of the map contains a building with valuable files.
The building is medium with a construction factor of 60 (6 for Alpha Strike), unless the players agree upon a different configuration.
The force earns 1,000,000 C-bills for every turn that they have the only infantry/Battle Armor units inside of the building at the end of the turn.

\item {\bfseries Assassination}: A local militia commander needs to be escorted across the battlefield.
The defender selects a medium or heavy 'Mech from the Periphery General or Pirates list.
The commander is a Gunnery 5/ Piloting 4 (Skill 4) pilot and half of the adjusted BV of the 'Mech counts against the defender's BV limit.
This 'Mech must cross the map from the defender's home edge to the attacker's home edge.
The attacker earns 7,000,000 C-bills if this 'Mech is destroyed or 3,500,000 C-bills if this 'Mech receives crippling damage.
The defender 7,000,000 C-bills if this 'Mech does not receive crippling damage or 3,500,000 C-bills if this 'Mech is crippled but not destroyed.

\end{enumerate}

Add the following sentences to the beginnig of p. 29 of the full rules and p. 10 of the quickstart rules:

These objectives may be adapted to best support the scenario format or the narative the players are creating, as long as all commanders agree.
When playing these objectives in Alpha Strike, 1 hex is equivalent to 2 inches and "in the same hex" means "in base to base contact".

\subsection{DropShip Customization - Maintenance}

Add the following sentence to the end of the first paragraph on p. 21 of the full rules:

Also, commanders may fix a limited number of through-armor critical hits or motive system damage without paying the \emph{repair} cost.

\subsection{Event Force Construction}

Add the following sentence to the fourth bullet point on p.4 of the Event rules:

If Battle Armor is not available to the faction in the era, then the force must contain at least one non-mechanized conventional infantry unit.
