Commanders may customize units by refitting an existing variant of a chassis.
The customized unit must use the same technology base as the variant of the chassis being customized and this technology base must be available to the force in this era.
All equipment or weapons added must be available in the current era.

The customized unit must be legal per \emph{BattleTech: TechManual} construction rules.
The unit retains the quirks of the chassis.
Major structural modifications such as changing the engine, cockpit, or internal structure are not permitted.
Partial wings, Triple Strength Myomer, and full head ejection systems cannot be added.

League organizers set the highest customization level allowed in the league.
Each customization level includes all levels below it.

\begin{description}

\item \emph{\bfseries Level 1}: Equipment and weapons may be removed from the unit.
Ammunition bins may be removed or converted to a different type of ammunition.
CASE may be added.
Additional armor may be added.

\item \emph{\bfseries Level 2}: Equipment, weapons, and ammunition bins may be moved to new locations.
Additional heat sinks may be added.
Infantry bays may be expanded.
Armor may be converted to standard or Ferro-Fibrous armor.

\item \emph{\bfseries Level 3}: Additional equipment may be added to the unit. 
MASC, a supercharger, or additional jump jets may be added.
Jump jets may be converted to improved jump jets.
Gyros can be replaced with another type of gyro.
Single heat sinks may be converted to double heat sinks.

\item \emph{\bfseries Level 4}: Armor may be converted to specialty armor, such as Stealth or Ferro-Lamellor.

\item \emph{\bfseries Level 5}: Additional weapons may be added to the unit.

\end{description}

A force can have multiple units with level 1 or level 2 customizations but only one unit with level 3 or higher customizations.
A unit with level 3 or higher customizations counts as the single Unique or Experimental unit allowed in a force; a force cannot have both a Unique or Experimental unit and a unit with level 3 or higher customizations.

Commanders purchase the base unit and then pay Tonnage / 4 for each level of customization past level 1 to customize the unit.
Custom units may be customized again.
If the custom unit uses Omni technology, the unit can still be reconfigured to other Omni variants of the base unit.

Customized units are more expensive to maintain.
Increase the to SP activity costs costs by 5\% for each level of customization past level 1.
For example, a unit with level 3 customization costs 10\% more to repair.

Custom units may be salvaged and sold but cannot be added to another force.
Commanders cannot acquire a custom unit from another force in any way.
Commanders may sell custom units per the standard rules.
