In order to use \emph{BattleTech: Instant Action} missions as casual scenarios for \emph{BattleTech: Outworlds Wastes}, first each side agrees upon a BV limit.
The standard \emph{BattleTech: Outworlds Wastes} limits of 6,000 BV for 1v1 or 10,000 BV for 2v2 agree with the recommendations for \emph{BatleTech: Instant Action}.

Next, both sides agree upon a Battlefield Support Points (BSP) budget and if Gambits and Conditions are being used.
BSP can be used with or without Gambits and Conditions, and Gambits and Conditions may be used with no other BSP, such as BSP Strikes.

Then, each side selects an agenda and consults the Mission Matrix to determine which mission corresponds to this pair of agendas.
Any special rules for the selected mission given in the Game Concepts section apply.
The mission determines the primary objective.

Finally, each side selects a secondary objective per the instructions in Secondary Objectives subsection of the Scenarios section for \emph{BattleTech: Outworlds Wastes}.

The secondary objective is scored as described in the Secondary Objectives subsection of \emph{BattleTech: Outworlds Wastes}.
The primary objective is scored as described below.

\begin{description}

\item {\bfseries Circle of Equals}: Each side receives a proportion of 5,000,000 C-bills based upon the ratio of the percentage of enemy BV \emph{destroyed} by each side.
Units that withdraw do not count as \emph{destroyed} for the purposes of scoring.
The side that has the last active units on the field during an End Phase, if any, receives an additional 2,000,000 C-bills.
For example, if the first side \emph{destroyed} 30\% of the enemy BV and the second side \emph{destroyed} 35\% of the enemy BV, then the first side receives 46.2\% of the C-bills and the second side receives 53.8\% of the C-bills.
The first side receives 2,307,692 C-bills and the second side receives 3,692,308 C-bills.
If the second side has the last active units on the field, then they receive an additional 2,000,000 C-bills.

\item {\bfseries Capture and Control}: Each side receives a proportion of 5,000,000 C-bills based upon the percentage of zones each side controls.
The side that controls the most zones, receives an additional 2,000,000 C-bills.
For example, if the Hold side controls 2 of the 3 Control Zones, then the Hold side receives 66.7\% of the 5,000,000 C-bills plus the 2,000,000 C-bills bonus and the Confront side receives the remaining 33.3\% of the 5,000,000 C-bills.
The Hold side 5,333,333 C-bills and the Confront side receives 1,666,667 C-bills.

\item {\bfseries Scanner Drop}: Each side receives a proportion of 5,000,000 C-bills based upon the percentage of target hexes with beacons placed.
The side that wins, receives an additional 2,000,000 C-bills.
For example, if the Recon side placed 4 beacons, then the Recon side receives 66.7\% of the 5,000,000 C-bills plus the 2,000,000 C-bills bonus and the Confront side receives 33.3\% of the 5,000,000 C-bills.
The Recon side receives 5,333,333 C-bills and the Confront side receives the remaining 1,666,667 C-bills.

\item {\bfseries Death before Dishonor}: Each side receives a portion of 7,000,000 C-bills based upon the status of the objective.
If the objective was destroyed, the Destroy side receives 7,000,000 C-bills.
If the objective was carried off the Destroy side's map edge, then the Confront side receives 7,000,000 C-bills.
Otherwise, each side receives 3,500,000 C-bills.

\item {\bfseries Take Intact}: Each side receives a proportion of 5,000,000 C-bills based upon the percentage of the Confront units except for the Prize that have suffered crippling damage.
Units that withdraw count as crippled for the purposes of scoring.
The side that won receives an additional 2,000,000 C-bills.
For example, if the Confront side has 6 units, then 1 of them is the prize and the remaining 5 are scored.
If 3 of the 5 non-Prize units suffered crippling damage, then the Salvage side receives 60.0\% of the 5,000,000 C-bills and the Confront side receives 40.0\% of the 5,000,000 C-bills.
The Salvage side receives 3,000,000 C-bills and the Confront side receives 2,000,000 C-bills.
If the Prize has been destroyed, immobilized, has lost a leg, or has had its MP reduced to 0, then the Salvage side receives an additional 2,000,000 C-bills, otherwise the Confront side receives an additional 2,000,000 C-bills.
If the Prize suffered crippling damage but was not destroyed, then the Salvage side may forgo all other \emph{salvage} to instead \emph{salvage} the Prize and add it to their list, paying only 30\% of the C-bill cost.

\item {\bfseries King of the Hill}: Each side receives a portion of 5,000,000 C-bills based upon the percentage of Victory Points each side earns.
The side with the most Victory Points, if any, receives an additional 2,000,000 C-bills.
For example, if the first side earned 6 Victory Points and the second side earned 8 Victory Points, then the first side receives 42.9\% of the 5,000,000 C-bills and the second side receives 57.1\% of the 5,000,000 C-bills plus the 2,000,000 C-bills bonus.
The first side receives 2,142,875 C-bills and the second side receives 4,857,142 C-bills.

\item {\bfseries Running Retreat}: Each side receives a proportion of 5,000,000 C-bills based upon the percentage of the Recon side's units that have been \emph{destroyed} or immobilized.
The side that wins receives an additional 2,000,000 C-bills.
Units that withdraw count as \emph{destroyed} for the purposes of scoring.
For example, if 45\% of the Recon side's units are \emph{destroyed} or immobilized, then the Hold side receives 45\% of the 5,000,000 C-bills, and the Recon side receives 55\% of the 5,000,000 C-bills plus the 2,000,000 C-bill bonus.
The Hold side receives 2,250,000 C-bills and the Recon side receives 4,750,000 C-bills.

\item {\bfseries Bombing Run}: Each side receives a proportion of 5,000,000 C-bills based upon the percentage of objectives delivered, out of 3 objectives.
The side that wins receives an additional 2,000,000 C-bills.
For example, if 2 objectives were delivered, then the Destroy side receives 66.7\% of the 5,000,000 C-bills and the Hold side receives 33.3\% of the 5,000,000 C-bills plus the 2,000,000 C-bill bonus.
The Destroy side receives 3,333,333 C-bills and the Hold side receives 4,666,667 C-bills.

\item {\bfseries One Man's Trash}: The side controlling the data core receives 7,000,000 C-bills at the end of the game.

\item {\bfseries Scout Clash}: Each side receives a portion of 5,000,000 C-bills based upon the percentage of Victory Points each side earns and winning the scenario.
The side that wins receives an additional 2,000,000 C-bills.
For example, if the first side earned 6 Victory Points and the second side earned 4 Victory Points, then the first side receives 60\% of the 5,000,000 C-bills plus the 2,000,000 C-bills bonus and the second side receives 40\% of the 5,000,000 C-bills.
The first side receives 5,000,000 C-bills and the second side receives 2,000,000 C-bills.

\item {\bfseries High Risk Extraction}: Each side receives a proportion of 5,000,000 C-bills based upon the percentage of agents removed, out of 3 agents.
The side that wins receives an additional 2,000,000 C-bills.
For example, if 2 agents were removed, then the Recon side receives 66.7\% of the 5,000,000 C-bills plus the 2,000,000 C-bills bonus and the Destroy side receives 33.3\% of the 5,000,000 C-bills.
The Recon side receives 5,333,333 C-bills and the Destroy side receives 1,666,667 C-bills.

\item {\bfseries Analyze or Recover}: Each side receives a portion of 5,000,000 C-bills based upon the percentage of their objectives they complete.
The side that wins receives an additional 2,000,000 C-bills.
For example, if the Recon side scanned 4 objectives, 66.7\% of their goal, and the second side left with 4 objectives, 100\% of their goal, then the first side receives 40\% of the 5,000,000 C-bills and the second side receives 60\% of the 5,000,000 C-bills plus the 2,000,000 C-bills bonus.
The first side receives 2,000,000 C-bills and the second side receives 5,000,000 C-bills.

\item {\bfseries Hot Potato}: The side not holding the objective at the end of the game receives 7,000,000 C-bills.
If side controlling the unit holding the objective at the end of the game has destroyed every enemy unit, then that side receives 7,000,000 C-bills.

\item {\bfseries Under No Circumstances}: Each side receives a proportion of 5,000,000 C-bills based upon the percentage of objectives removed or destroyed.
The side that wins receives an additional 2,000,000 C-bills.
For example, if 2 objectives were removed and 3 objectives were destroyed, then the Salvage side receives 40\% of the 5,000,000 C-bills and the Destroy side receives 60\% of the 5,000,000 C-bills plus the 2,000,000 C-bills bonus.
The Salvage side receives 2,000,000 C-bills and the Destroy side receives 7,000,000 C-bills.

\item {\bfseries Get The Goods}: Each side receives a portion of 5,000,000 C-bills based upon the percentage of Victory Points each side earns.
The side that wins receives an additional 2,000,000 C-bills.
For example, if the first side earned 6 Victory Points and the second side earned 6 Victory Points, then the first side receives 50\% of the 5,000,000 C-bills and the second side receives 50\% of the 5,000,000 C-bills.
Neither side earns the 2,000,000 C-bill bonus.
The first side receives 2,5000,000 C-bills and the second side receives 2,500,000 C-bills.

\end{description}
