Commanders may customize their DropShip to better support their force.
Commanders are encouraged to name their DropShip before using this rule.
Commanders should keep track of their DropShip customizations, as shown on the \ifthenelse{\equal{\outworldsMode}{mode-web}}{sample \hyperref[sec:sample_dropship]{DropShip tracking}}{\emph{Sample DropShip Customization Tracking} (see p. \pageref{sec:sample_dropship})}.

Commanders can customize their DropShips in the following categories:

\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\begin{multicols}{2}}{}

\begin{itemize}

  \item 'Mech Maintenance

  \item Ground Combat Vehicle Maintenance

  \item VTOL Combat Vehicle Maintenance

  \item Aerospace Unit Maintenance

  \item ProtoMech Maintenance

  \item Machine Shop

  \item Medical Bay

  \item Infantry Quarters

  \item Simulators

  \item Bay Configuration Limits

\end{itemize}

\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\end{multicols}}{}

Each commander receives 5 customization points to modify their DropShip.
The DropShip starts at level 0 in each category.
Commanders spend customization points to raise the level for a category and gain the corresponding benefit.
Any portion of the initial 5 customization points may be reserved for future use.
The table below details how many points it costs to increase a category customization level.

\begin{table}[!h]
  \ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
  \centering
  \newcolumntype{L}[1]{>{\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

  \begin{tabular}{!{\vrule width 1pt} m{9em} L{9em} !{\vrule width 1pt}}
    \Hline{1pt}
    \rowcolor{black!30} \bfseries{Level Increase} & \bfseries{Cost} \\
    \Hline{1pt}
    Level -2 to -1 & 2 point cost \\
    Level -1 to  0 & 1 point cost \\
    Level  0 to  1 & 1 point cost \\
    Level  1 to  2 & 2 point cost \\
    Level  2 to  3 & 3 point cost \\
    \Hline{1pt}
  \end{tabular}

  \caption*{DropShip Customization Point Costs}
\end{table}

Point costs are cumulative.
For example, it costs 1 point to go from level 0 to level 1 and 2 points to go from level 1 to level 2, so it costs 3 total points to go from level 0 to level 2.

Commanders can further customize their DropShip, but space and resources must be reallocated from one category to another.
After each contract, commanders may spend 50 SP to decrease the level of one or more categories to earn sufficient customization points and increase the level of a single category.
The customization points earned when decreasing the level of a category are given in the table below.
This may be done only once between contract.

\begin{table}[!h]
  \ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
  \centering
  \newcolumntype{L}[1]{>{\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

  \begin{tabular}{!{\vrule width 1pt} m{9em} L{9em} !{\vrule width 1pt}}
    \Hline{1pt}
    \rowcolor{black!30} \bfseries{Level Decrease} & \bfseries{Payout} \\
    \Hline{1pt}
    Level -1 to -2 & 2 points earned \\
    Level  0 to -1 & 1 point earned  \\
    Level  1 to  0 & 1 point earned  \\
    Level  2 to  1 & 2 points earned \\
    Level  3 to  2 & 3 points earned \\
    \Hline{1pt}
  \end{tabular}

  \caption*{DropShip Customization Point Payouts}
\end{table}
