\ifthenelse{\equal{\outworldsMode}{mode-pdf-event}} {
% Event rules PDF
These rules cover background information, player rules, event organizer information, and reference material.
The background information describes the Outworlds Wastes region and the \emph{BattleTech: Outworlds Wastes} rules.
\emph{Force Construction} (see p. \pageref{subsec:event_force_construction}) and \emph{Force Maintenance and Improvements} (see p. \pageref{subsec:event_force_maintenance}) are the minimum rules needed for a player to begin Outworlds Wastes league play.
Scoring rules are provided for event organizers.
The reference materials include a region map and list of references.
} {
\ifthenelse{\equal{\outworldsMode}{mode-web}} {
% Website
This website covers background information, player rules, league organizer information, event rules, and reference material.

To start with smaller scale event play, where each commander controls a mixed combined arms lance, read the \hyperref[sec:event_play]{Event Play} rules.
Sample scenarios are available as \hyperref[sec:downloads]{downloads} and the Event Play rules include instructions on creating additional scenarios.

For \hyperref[sec:league_play]{League Play} where each commander controls a combined arms company, see the \hyperref[subsec:force_construction]{Force Construction} and \hyperref[subsec:force_maintenance]{Force Maintenance and Improvements} rules.
Optional advanced force construction and force management rules are also included
Sample scenarios are available as \hyperref[sec:downloads]{downloads} and the \hyperref[sec:scenarios]{scenarios} rules include instructions on creating additional scenarios.

The reference materials include a region \hyperref[sec:outworlds_wastes_map]{map}, sample \hyperref[sec:sample_tracking_event]{event} and \hyperref[sec:sample_tracking]{league} force tracking sheets, and a list of \hyperref[sec:references]{references}.
} {
% Full and quickstart rules PDF
These rules cover background information, player rules, league organizer information, and reference material.
The background information describes the Outworlds Wastes region and the \emph{BattleTech: Outworlds Wastes} rules.
\emph{Force Construction} (see p. \pageref{subsec:force_construction}) and \emph{Force Maintenance and Improvements} (see p. \pageref{subsec:force_maintenance}) are the minimum rules needed for a player to begin Outworlds Wastes league play.
Scenario design and league scoring rules are provided for league organizers.
The reference materials include a region map, a list of references, and sample tables for tracking a commander's forces.
}}
