Commanders create an initial force of up to 10,000 BV.
BV costs for all units are listed in the \href{http://www.masterunitlist.info}{Master Unit List} or \href{https://megamek.org}{MegaMekLab}.
Force construction must follow the following rules:

\begin{itemize}

\item Commanders have a modified Union class DropShip with 15 configurable bays.
Bays may be empty and can changed to a different configuration.
Bay space for all infantry units is shared across bays.
Your entire force must fit onto your DropShip.
Bay limits are in the table below.

\begin{table}[!h]
\ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
\centering
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\begin{tabular}{!{\Vline{1pt}} m{10em} m{20em} R{3.8em} !{\Vline{1pt}}}
\Hline{1pt}
\rowcolor{black!30}  \bfseries{Bay Type} & \bfseries{Capacity} & \bfseries{Limit} \\
\Hline{1pt}
'Mech            & 1 'Mech or 1/2 superheavy 'Mech    & 12 bays \\
Combat Vehicle   & 2 vehicles or 1 superheavy vehicle & 5 bays  \\
Aerospace        & 1 aerospace unit                   & 2 bays  \\
ProtoMech        & 5 ProtoMechs                       & 2 bays  \\
Infantry         & 15 tons or 1 unit over 15 tons     & 2 bays  \\
\Hline{1pt}
\end{tabular}
\caption*{DropShip Bay Limits}
\end{table}

Support, Advanced Support, and Advanced Aerospace units are not permitted.
Illegal designs and units over 200 tons are also not permitted.
Units over 100 tons, such as superheavy 'Mechs, require double the bay space as standard units.

\item Commanders must select units from their faction on the \href{http://www.masterunitlist.info/}{Master Unit List} for the era chosen by league organizers.
Forces can include units with introductory, standard, or advanced technology.
For example, the Marauder MAD-3R is a valid ilClan era mercenary unit.

\item Forces may include one Unique or Experimental unit.
The Unique unit may be Extinct if another variant of the unit is available to the faction in the current era and the faction has the relevant technology base to recreate the unit.

\item Each force can start with no more than 7,000 BV in 'Mechs.
Commanders are encouraged to try to use the typical 'Mech unit composition of their faction.

\item Some scenarios will require infantry/Battle Armor or Combat Vehicles with cargo capacity, so commanders should have at least one of each of these units in their force.

\item Unless optional Battlefield Support or off-board artillery rules are used, a force can only include on-map units.
For example, artillery and aerospace units can only be used on-map by default.

\item The BV cost of a unit includes the skill level.
The initial skill levels for a unit may be no better than Gunnery 3/Piloting 4 and cannot differ by more than 3.
Average skill levels for factions and units are given on \emph{BattleTech: Total Warfare} p. 40.
ProtoMechs always have Piloting 5 and infantry units without anti-'Mech equipment have Anti-'Mech 5, because these skills are not used for these units.

\end{itemize}

Commanders are responsible for knowing which rulebooks contain the rules pertaining to all units and special equipment in their force.

Unit record sheets can be generated using \href{https://megamek.org}{MegaMekLab} or similar tools.
BV costs sometimes do not mach between the \href{http://www.masterunitlist.info}{Master Unit List} and \href{https://megamek.org}{MegaMekLab}, especially for infantry units.
Commanders must use the same source for all BV costs.
All record sheets must agree with the BV costs from this source.

Learning new types of units can be intimidating.
Commanders may limit the types of different units in their non-'Mech forces.
For example, a force could include only troop transports and Battle Armor so the commander can meet any objectives while keeping new rules to a minimum.
