For Event Play, commanders start with a Scale 1 force and each track is played at Scale 1.
You start with 3,500 BV (125 PV) to acquire initial units for your force and a Warchest of 3,000 SP.
BV (PV) costs for all units are listed in the \href{http://www.masterunitlist.info}{Master Unit List} or \href{https://megamek.org}{MegaMekLab}.
Force construction must follow these rules:

\begin{itemize}

  \item You have a modified DropShip, similar to a Trojan, with 8 configurable bays.
    Bays may be empty and can changed to a different configuration.
    Your entire force must fit onto your DropShip.
    Bay limits are in the table below.

  \begin{table}[!h]
    \ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
    \centering
    \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

    \begin{tabular}{!{\Vline{1pt}} m{10em} m{20em} R{3.8em} !{\Vline{1pt}}}
      \Hline{1pt}
      \rowcolor{black!30} \bfseries{Bay Type} & \bfseries{Capacity} & \bfseries{Limit} \\
      \Hline{1pt}
      'Mech          & 1 'Mech or 1/2 superheavy 'Mech    & 6 bays \\
      Combat Vehicle & 2 vehicles or 1 superheavy vehicle & 3 bays \\
      ProtoMech      & 5 ProtoMechs                       & 1 bay  \\
      Infantry       & 15 tons or 1 unit over 15 tons     & 1 bay  \\
      \Hline{1pt}
    \end{tabular}

    \caption*{Event Play DropShip Bay Limits}
  \end{table}

  \item You must select units from one faction on the \href{http://www.masterunitlist.info/}{Master Unit List} for the era chosen by event organizers.
    Forces may include units with introductory, standard, and advanced technology.
    Custom, experimental, and unique units are not permitted.

  \item Each force must have at least one 'Mech.
    Your initial force may have no more than two 'Mechs.
    'Mechs can account for no more than 3,000 BV (100 PV).

  \item Each force must have at least one Battle Armor unit.
    If Battle Armor is not available to the faction in the era, then the force must contain at least one non-mechanized conventional infantry unit.

  \item Each force must have one unit capable of carrying the Battle Armor (or infantry) unit.
    An OmniMech can carry standard Battle Armor.
    BattleMechs can carry Battle Armor equipped with magnetic clamps, but receive a -1 MP (-2 inch) reduction to their Walking MP (p. 227, \emph{TW}, p. 39, \emph{AS: CE}).

  \item You may play non-'Mech units as Battlefield Support: Assets; however Assets cannot score objectives.

  \item Your force cannot contain artillery, aerospace, or other support units.
    However, you may have access to Battlefield Support: Strikes for some tracks.

  \item The BV costs of a unit must be modified to include C\textsuperscript{3} and TAG.

  \item The BV (PV) costs do not include Skill Advances.
    All units start at 4 Gunnery and 5 Piloting/Driving/Anti-'Mech (Skill 4).
    ProtoMechs always have Piloting 5 and infantry units without anti-'Mech equipment have Anti-'Mech 5.
    You start with two Skill Advances (one Skill Advance for Alpha Strike); however these advances cannot be applied to the same skill on the same unit.

\end{itemize}
