For League Play, commanders start with a Scale 3 force but each track is played at Scale 2.
You start with 11,000 BV (400 PV) to acquire initial units for your force and a Warchest of 3,000 SP.
BV costs for all units are listed in the \href{http://www.masterunitlist.info}{Master Unit List} or \href{https://megamek.org}{MegaMekLab}.
Force construction must follow the following rules:

\begin{itemize}

  \item Commanders have a modified class DropShip, similar to a Union, with 15 configurable bays.
    Bays may be empty and can changed to a different configuration.
    Bay space for all infantry units is shared across bays.
    Your entire force must fit onto your DropShip.
    Bay limits are in the table below.

  \begin{table}[!h]
    \ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
    \centering
    \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

    \begin{tabular}{!{\Vline{1pt}} m{10em} m{20em} R{3.8em} !{\Vline{1pt}}}
      \Hline{1pt}
      \rowcolor{black!30}  \bfseries{Bay Type} & \bfseries{Capacity} & \bfseries{Limit} \\
      \Hline{1pt}
      'Mech          & 1 'Mech or 1/2 superheavy 'Mech    & 12 bays \\
      Combat Vehicle & 2 vehicles or 1 superheavy vehicle & 5 bays  \\
      Aerospace      & 1 aerospace unit                   & 2 bays  \\
      ProtoMech      & 5 ProtoMechs                       & 2 bays  \\
      Infantry       & 15 tons or 1 unit over 15 tons     & 2 bays  \\
      \Hline{1pt}
    \end{tabular}

    \caption*{League Play DropShip Bay Limits}
  \end{table}

    Support, Advanced Support, and Advanced Aerospace units are not permitted.
    Illegal designs and units over 200 tons are also not permitted.
    Units over 100 tons, such as superheavy 'Mechs, require double the bay space as standard units.

  \item You must select units from their faction on the \href{http://www.masterunitlist.info/}{Master Unit List} for the era chosen by league organizers.
    Forces can include units with introductory, standard, or advanced technology.
    For example, the Marauder MAD-3R is a valid ilClan era mercenary unit.

  \item Forces may include one Unique or Experimental unit.
    The Unique unit may be Extinct if another variant of the unit is available to the faction in the current era and the faction has the relevant technology base to recreate the unit.

  \item Each force can start with no more than 7,000 BV (250 PV) in 'Mechs.
    You are encouraged to try to use the typical 'Mech unit composition of their faction.
    Organizers may raise this limit to 9,000 BV (300 PV) if they want to de-emphasize combined arms for their league.

  \item Some scenarios will require infantry/Battle Armor or Combat Vehicles with cargo capacity, so commanders should have at least one of each of these units in their force.
    You may play these units as Battlefield Support: Assets; however Assets cannot score objectives.

  \item In order to use Battlefield Support: Strikes, your command must have a unit capable of offering the support.
    At least 500 BV (25 PV) must be spent on units capable of offering Battlefield Support: Strikes.

  \begin{table}[!h]
    \ifthenelse{\not \equal{\outworldsMode}{mode-web}}{\fontfamily{Montserrat-LF}}{\small}\selectfont
    \centering
    \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

    \begin{tabular}{!{\Vline{1pt}} m{18em} m{20em} !{\Vline{1pt}}}
      \Hline{1pt}
      \rowcolor{black!30}  \bfseries{Support Type} & \bfseries{Required Unit} \\
      \Hline{1pt}
      Offensive Aerospace Support   & Attack or fire-support aerospace unit    \\
      Defensive Aerospace Support   & Dogfighter or interceptor aerospace unit \\
      Artillery Support             & Corresponding artillery unit             \\
      Minefield Support             & Any unit                                 \\
      \Hline{1pt}
    \end{tabular}

    \caption*{Support Unit Requirements}
  \end{table}

  \item The BV (PV) costs do not include Skill Advances.
    All units start at 4 Gunnery and 5 Piloting/Driving/Anti-'Mech (Skill 4).
    ProtoMechs always have Piloting 5 and infantry units without anti-'Mech equipment have Anti-'Mech 5.
    You start with two Skill Advances (one Skill Advance for Alpha Strike); however these advances cannot be applied to the same skill on the same unit.

\end{itemize}
