The \href{http://www.masterunitlist.info/}{Master Unit List} lists all major official BattleTech factions.
Commanders may create a custom faction list for their force.

To create a custom faction list, go to the \href{http://www.masterunitlist.info/Unit/Filter}{Units Tab on Master Unit List}.
Filter the units to include one faction list and one general list for the current league era.
For example, the Pirates faction by default typically includes the Periphery General list.
A Dark Caste custom faction could include the Pirates faction list with the Inner Sphere Clan General list.

All restrictions from the basic Force Construction rules, such as DropShip bay limits and only including one Unique or Experimental unit in a force, still apply.

If a faction does not have a general list, then it cannot be customized in this way.
Factions without a general list include Mercenary, Kell Hounds, Wolf's Dragoons, and Society.
These factions have the phrase "including Blank General List" on their faction and era specific pages.
Adding a general list to these factions would give the commander a disproportionately large number of units to choose from.

Commanders can still create a custom mercenary faction with these Advanced Force Construction Rules.
First select a faction list for the region in which the force was founded or primarily operates and then pick an appropriate general list.
For example, a mercenary force that was founded in the Draconis Combine but moved to the Periphery after Coordinator Takashi Kurita's \emph{Death to Mercenaries} edict could use Draconis Combine faction list with the Periphery General list.

League organizers may allow additional adjustments, such as allowing a commander to use two faction lists instead of one faction list and one general list.
Any additional adjustments must be available to all commanders.
