\item {\bfseries Advanced Refit}: Pay 200\% of the difference in C-bill cost to refit a unit to a different variant that is available on a different faction list.
The unit must be available in the current era.
A Locust LCT-1V is a widely available variant that costs 1,512,400 C-bills while the Locust LCT-6M costs 4,277,500 C-bills is only available to the Free Worlds League and the Word of Blake during the Civil War era.
A commander outside of the Free Worlds League or Word of Blake may pay 5,530,200 C-bills to convert a LCT-1V to a LCT-6M.
Converting back to a variant on the faction list for the force only costs the standard \emph{Refit} cost.
\emph{Advanced Refit} has a minimum cost of 500,000 C-bills or 20\% of the original C-bill cost of the unit, whichever is less.

\emph{Advanced Refit} can also be used to convert a unit a unique or experimental variant, if the force does not already contain a unique or experimental unit.
See the \ifthenelse{\equal{\outworldsMode}{mode-web}}{\hyperref[subsec:force_construction]{Force Construction} rules}{\emph{Force Construction} rules (p. \pageref{subsec:force_construction})} for restrictions on the single unique or experimental unit in a force.

There is not cost when using \emph{Advanced Refit} to permanently reduce the size of a Battle Armor or infantry unit, such as reducing a salvaged Elemental point with 5 troops to an Inner Sphere squad size of 4 troops.
Increasing the size of a Battle Armor or infantry unit still incurs the double cost penalty if the unit is from a different faction list; for example refitting a salvaged Gray Death Scout Suit squad with 4 troops to a 5 troop point would cost 1,040,160 C-bills for a faction that does not have the Gray Death Scout Suit on their faction list.

\item {\bfseries Advanced Omni Refit:} An \emph{Omni Refit} allows units to be temporarily converted to a cheaper variant for a scenario at no cost.
This variant must be available in the current era but does not need to be on the force's faction list.
Refitting is required to use more expensive variants.
As with the \emph{Advanced Refit}, pay 200\% of the difference in C-bill cost to refit a unit to a more expensive variant that is available on a different faction list.
Once the unit has been converted, it can be temporarily configured as a cheaper variant for a scenario at no cost.
