\item {\bfseries Custom Units}: Commanders may customize units by refitting an existing variant of a chassis.
The customized unit must use the same technology base as the variant of the chassis being customized and this technology base must be available to the force in this era.
All equipment or weapons added must be available in the current era.

The customized unit must be legal per \emph{BattleTech: TechManual} construction rules.
The unit retains the quirks of the chassis.
Major modifications such as changing the engine, gyro, and internal structure are not permitted.
Partial wings, Triple Strength Myomer, and full head ejection systems cannot be added.

League organizers set the highest customization level allowed in the league.
Each customization level includes all levels below it.

\begin{description}

\item \emph{\bfseries Level 1}: Equipment and weapons may be removed from the unit.
Ammunition bins may be removed or converted to a different type of ammunition.
CASE may be added.
Additional armor may be added.

\item \emph{\bfseries Level 2}: Equipment, weapons, and ammunition bins may be moved to new locations.
Additional heat sinks may be added.
Infantry bays may be expanded.
Armor may be converted to standard or Ferro-Fibrous armor.

\item \emph{\bfseries Level 3}: Additional equipment may be added to the unit, to include MASC or a supercharger.
Single heat sinks may be converted to double heat sinks.

\item \emph{\bfseries Level 4}: Armor may be converted to specialty armor, such as Stealth or Ferro-Lamellor.

\item \emph{\bfseries Level 5}: Additional weapons may be added to the unit.

\end{description}

A force can have multiple units with level 1 or level 2 customizations but only one unit with level 3 or higher customizations.
A unit with level 3 or higher customizations counts as the single Unique or Experimental unit allowed in a force; a force cannot have both a Unique or Experimental unit and a unit wit level 3 or higher customizations.

Commanders purchase the base unit and then pay 200\% of the difference in C-bill cost of the original unit and the computed C-bill cost of the custom unit.
Customization has a minimum cost of 500,000 C-bills or 20\% of the original C-bill cost of the unit, whichever is less.
Custom units may be customized again.
If the custom unit uses Omni technology, the unit can still be configured as a cheaper Omni variant of the chassis at no cost.

Customized units are more expensive to maintain.
Increase the \emph{Repair} and \emph{Replace} costs by 5\% for each level of customization past level 1.
For example, a unit with level 3 customization costs 10\% more to \emph{Repair} and \emph{Replace}; repairs cost of 35\% of the C-bill cost and replacement costs 60\% of the C-bill cost.

Custom units cannot be purchased as salvage but selling a salvaged custom unit earns 25\% of the computed C-bill cost.
Commanders cannot purchase a custom unit from another commander.
Commanders can sell this custom unit for parts at 40\% of the C-bill cost, or 20\% of the C-bill cost if the unit is destroyed.
