League organizers may advance the league to a new era.
Commanders may create a new force or continue to play their current force in the new era.

If the force's faction is not available in the new era, then the commander must pick a new faction list.
The commander has three options for selecting a new faction list.

\begin{itemize}

\item If the faction becomes part of a new faction, then the new faction list may be used.
For example, Clan Snow Raven and the Outworlds Alliance merge to form the Raven Alliance during the Republic era.
Most Snow Raven and Outworlds Alliance forces would become Raven Alliance forces.

\item A commander may select an allied faction.
The St. Ives Compact was forcefully reintegrated into the Capellan Confederation in 3063.
A St. Ives Compact commander may decide to join the Federated Suns instead of joining the Capellan Confederation.
The new faction should share the same general list or historically be allies of the old faction.

\item A commander may decide to become a mercenary or pirate.
Their force would use the mercenary or pirate faction list.

\end{itemize}

Unit variants that are extinct but still have alternate variants in the current era can be maintained and improved as usual.
Units that are fully extinct in the new era cost 10\% more to maintain and cannot be replaced.
The following additional rules apply to maintaining extinct units.

\begin{description}

\item {\bfseries Repair}: If no variant of the unit exists in the current era, then repairing the unit costs 35\% of the C-bill cost instead of 25\% of the C-bill cost.

\item {\bfseries Replace}: If no variant of the unit exists in the current era, then the unit cannot be replaced.

\item {\bfseries Recruit}: If no variant of the unit exists in the current era, then recruiting new troops to replace troops in an infantry or Battle Armor unit costs 60\% of the cost for a single troop.
At least one troop in the unit must survive in order to recruit new troops, otherwise the unit is considered \emph{destroyed}.

\item {\bfseries Salvage}: Extinct units you destroyed in a scenario can only be sold for 25\% cost.

\item {\bfseries Sell}: Extinct units can be sold at 50\% of the C-bill cost, or 25\% of the C-bill cost if destroyed.

\end{description}
