You command a combined arms force exploring the Outworlds Wastes for your faction and compete with other factions in the Outworlds Wastes to grow your force and recover lost technology.
Common factions for the region include:

\begin{itemize}

  \item {\bfseries Outworlds Alliance}: A resourceful faction focused on reclaiming lost resources to support their remaining systems who was founded by frontier settlers and isolationists.

  \item {\bfseries Clan Snow Raven}: An opportunistic and efficient clan, recently arrived from the Homeworlds, that is seeking to eek out an existence in the abandoned worlds of the Outworlds Alliance. 

  \item {\bfseries Draconis Combine}: A fiercely loyal and aggressive faction with a culture rooted in the code of the samurai and focused on honor and conquest.

  \item {\bfseries Federated Suns}: A pragmatic faction balancing diplomacy and military action that is inspired by European knightly orders and chivalry.

  \item {\bfseries Mercenary groups}: Flexible and opportunistic forces driven by profit, holding shifting allegiances, and inspired by historical mercenaries and free companies.

  \item {\bfseries Pirate gangs}: Outlaws motivated by greed, power, and the freedom from any government oversight living under the code of might is right. 

  \item {\bfseries Clan Dark Caste}: Clan bandits, renegades, and malcontents doing what they must to survive while utilizing stolen or scavenged Clan equipment.

\end{itemize}

These factions are the most prevalent in the region, but many other factions may be found in the Outworlds Wastes.
You may pick the faction any find interesting.
