The general background, goals, and playstyles of the common factions in the Outworlds Wastes are outlined below.
You may use these descriptions as inspiration for their forces but are not limited to the notes given here.

{\bfseries Outworlds Alliance}:
The Outworlds Alliance has always prioritized survival over expansion, especially during and after the devastating Succession Wars.
They now focus on reclaiming lost resources to support their struggling systems.
Commanders from the Alliance are tasked with recovering critical supplies and technology to bolster their defense against external threats and internal collapse.
Known for their pacifist roots, they often prefer defensive tactics and only striking when absolutely necessary.

\emph{Playstyle}:
Focus on logistics, careful planning, and defensive positions rather than direct engagement.
Ideal for commanders who enjoy longer-term strategies and avoiding unnecessary risks.

{\bfseries Clan Snow Raven}:
Clan Snow Raven is driven by a desire to rebuild after its abjuration from the Clan Homeworlds and sees the Outworlds Wastes as a prime opportunity.
They focus on claiming new systems to expand their influence and gather valuable Star League technology.
Snow Raven commanders are highly disciplined and use air and space superiority to outmaneuver opponents, prioritizing the acquisition of territory and technology to fuel their efforts to solidify their position.

\emph{Playstyle}:
High-tech and strategic, emphasizing mobility, air and space superiority, and tech acquisition.
Perfect for commanders who enjoy a blend of aggressive expansion and tactical flexibility.

{\bfseries Draconis Combine}:
Steeped in a warrior code inspired by samurai traditions, the Draconis Combine is driven by a fierce sense of honor.
In the Outworlds Wastes, their mission is simple: conquer and claim LosTech to bolster their military strength.
Combine commanders prioritize direct confrontation and see each battle as an opportunity to prove their worth.
They view the Wastes as a battleground to extend their reach and crush opposition, especially from rival factions like the Federated Suns.

\emph{Playstyle}:
Aggressive and honor-bound, favoring heavily armed forces and head-on confrontations.
Best for commanders who enjoy straightforward combat and maintaining a strong offensive presence.

{\bfseries Federated Suns}:
The Federated Suns, driven by their knightly traditions, see the Outworlds Wastes as an opportunity to bolster their interests.
Their primary goals are to secure vital resources and prevent hostile factions, like the Draconis Combine, from gaining a foothold.
Suns commanders are pragmatic, blending diplomacy with force and willing to negotiate to secure strategic advantages.
In the Wastes, they're known for their adaptability and readiness to seize opportunities to strengthen their position.

\emph{Playstyle}:
Balanced and tactical with the flexibility to switch between diplomacy and military action.
Ideal for commanders who enjoy a mix of negotiation and combat while focusing on securing objectives.

{\bfseries Mercenary Groups}:
Mercenaries are drawn to the Outworlds Wastes for one reason: profit.
These opportunistic groups are willing to work for the highest bidder and constantly shifting allegiances based on who offers the most C-bills.
Mercenary commanders are flexible and resourceful, using whatever means necessary to achieve their goals.
Whether hired to scout for LosTech or protect corporate interests, mercenaries thrive in the chaos of the Wastes, adapting quickly to ever-changing circumstances.

\emph{Playstyle}:
Flexible and opportunistic, capable of switching tactics and allegiances on the fly.
Ideal for commanders who enjoy a wide range of strategies and unpredictable engagements.

{\bfseries Pirate Gangs}:
The lawless regions of the Outworlds Wastes are a haven for pirate gangs.
These ruthless raiders strike quickly and without warning, plundering resources and tech from vulnerable forces.
Pirates prefer hit-and-run tactics, avoiding drawn-out battles in favor of rapid strikes that leave their enemies reeling.
They operate on the fringes, exploiting the lack of central authority and preying on isolated outposts.
In the Wastes, pirate commanders thrive on chaos and the spoils of war.

\emph{Playstyle}:
Fast and unpredictable, focusing on hit-and-run tactics and opportunistic strikes.
Best for commanders who prefer guerrilla warfare and ambushing unsuspecting opponents.

{\bfseries Clan Dark Caste}:
Outcasts from the rigid Clan structure, the Dark Caste is made up of warriors who have been shunned by their brethren.
Now, they survive on the fringes of Clan society, scavenging for resources and using unconventional tactics to stay one step ahead of both Clans and Inner Sphere forces.
In the Outworlds Wastes, Dark Caste commanders are desperate, using guerrilla warfare and sabotage to maintain their independence and scrape together the resources they need to survive.

\emph{Playstyle}:
Desperate and unconventional, relying on sabotage, guerrilla tactics, and scavenging.
Perfect for commanders who enjoy asymmetric warfare and surviving against the odds.
