In competitive play, commanders play a series of scenarios in a Swiss-system tournament.

A commander can only use a single force for the tournament.
League organizers may require new forces for the tournament or allow forces that have been used in casual play.

Any optional or advanced rules must be agreed upon in advance and consistent across the tournament play.
For example, league organizers could permit \emph{Advanced Refit} rules while disallowing \emph{Design Quirks} and \emph{Special Pilot Abilities} for the tournament.

The scenarios in the tournament should only be 1v1.
Each commander should play a different opponent during each scenario, if possible.
The last scenario should be a large scale event that requires a significant portion of each commander's forces.

Commanders may only use C-bills earned during the tournament to repair and update their forces per the Force Maintenance and Improvements rules after a scenario.
League organizers may give forces an initial maintenance budget.

Each 1,000,000 C-bills earned during a scenario is worth 1 point for scoring.
The C-bills earned includes primary objectives, secondary objectives, and salvage.
The players rankings are updated after each scenario.
Ties are broken by the lowest total BV lost across all scenarios thus far, which \emph{destroyed} units counting as their full BV and units in \emph{forced withdrawal} counting as half their full BV.

At the end of these scenarios, winners are determined by their ranking.
Additional winners may be determined for specific categories, such as Best Painted Force or Best Force Lore.
