Commanders start with 10,000 BV to acquire initial units for their force.
BV costs for all units are listed in the \href{http://www.masterunitlist.info}{Master Unit List} or \href{https://megamek.org}{MegaMekLab}.
Force construction must follow these rules:

\begin{itemize}

\item Commanders have a modified Union class dropship with 16 configurable bays.
Each bay can hold 1 'Mech, 2 Combat Vehicles, 2 aerospace units, 5 ProtoMechs, 1 mechanized infantry unit, or 5 tons of Battle Armor/non-mechanized infantry.
Bay space for all Battle Armor and non-mechanized infantry units is shared; for example, 4 bays can hold 20 tons, which is 5 squads of Inner Sphere Standard Battle Armor.
The dropship may have no more than 12 'Mech bays, 5 Combat Vehicle bays, 2 aerospace bays, 2 ProtoMech bays, or 5 infantry/Battle Armor bays.
Bays can be empty or changed between configurations.
Your entire force must fit onto your dropship.

\item Commanders should select units from their faction on the \href{http://www.masterunitlist.info/}{Master Unit List} for the era chosen by league organizers.
Forces can include units with introductory, standard, and advanced technology.
For example, the Marauder MAD-3R, Marauder MAD-7R, and Marauder II MAD-6C are legal ilClan era mercenary units while the Marauder II MAD-6M is not.

\item Forces can include one Unique or Experimental unit.
The Unique unit may be Extinct if another variant of the unit is available in the current era and the faction has access to the relevant technology base needed to recreate the unit.

\item Each force can start with no more than 7,000 BV in 'Mechs.
Commanders are encouraged to try to use the typical 'Mech unit composition of their faction.
However, this can be difficult to accomplish for Clan or ComStar forces, so this is not a requirement.

\item Each force can include any number of supporting units, such as Combat Vehicles, ProtoMechs, Battle Armor, and infantry, so long as the dropship bay restrictions are met.
Some scenarios will require infantry/Battle Armor or Combat Vehicles with cargo capacity, so commanders should have at least one of each of these units in their force.

\item Forces cannot contain off-map battlefield support units, such as artillery or aerospace fighters.
However, forces can contain any on-map units, to include on-map artillery.

\item The BV costs of a unit includes the skill levels.
Skill levels should generally be close to the average skill levels given on page 40 of \emph{BattleTech: Total Warfare}.
The skill levels for a unit may be no better than Gunnery 3/Piloting 4 initially.
ProtoMechs and mechanized infantry always have Piloting/Anti-'Mech 5, because these skills are not used for these units.

\end{itemize}

One of the goals of the Outworlds Wastes framework is to explore different equipment.
Commanders are encouraged to know where in the rule books other commanders can read about the rules pertaining to any special equipment for units in their force.
Unit record sheets can be generated using \href{https://megamek.org}{MegaMekLab} or similar tools.

Learning new types of units can be intimidating, especially in Total Warfare.
Commanders are welcome to limit the number of types of units in their non-'Mech forces.
For example, a force could include only troop transports and Battle Armor so the commander can meet any objective while keeping new rules to a minimum.
