Commanders can spend C-bills they earn in scenarios to improve their force.
Possible improvements are listed below.
C-bill costs for all units are listed on the \href{http://www.masterunitlist.info}{Master Unit List}.
The C-bill cost in \href{https://megamek.org}{MegaMekLab} can be used if the \href{http://www.masterunitlist.info}{Master Unit List} does not list a cost.

\begin{itemize}

\item {\bfseries Train}: Pay 500,000 C-bills multiplied by the difference in BV skill multiplier to improve a unit's skill levels.
For example, a Gunnery 4/Piloting 5 pilot has a BV skill multiplier of 1.0 and a 3/4 pilot has a BV skill multiplier of 1.32.
Therefore, it costs 160,000 C-bills to train a 4/5 pilot to be a 3/4 pilot.
All units cannot be upgraded past 1/2.
New units cannot be upgraded past 3/4.
Old units that did not participate in the most recent scenario cannot be upgraded past 4/5.
See \emph{BattleTech: TechManual}, page 315, for the BV skill multiplier table.
A unit's skill levels can be degraded at no C-bill cost.
ProtoMechs and mechanized infantry always have Piloting/Anti-'Mech 5.

\item {\bfseries Replace}: Pay 50\% of the C-bill cost, rounded up, to replace a \emph{destroyed} unit.
If the 'Mech pilot or vehicle crew was killed, the replacement cost includes a 5/6 pilot or crew.
If an entire infantry or Battle Armor unit was destroyed, the replacement cost includes 5/6 troops.
The ProtoMech replacement cost includes a 5/6 pilot.
The new unit can be trained as above.
See \emph{BattleTech: Total Warfare} for the definition of \emph{destroyed} for different types of units.

\item {\bfseries Repair}: Pay 25\% of the C-bill cost, rounded up, to repair all internal damage and critical components for a unit that has not been \emph{destroyed}.
If the pilot or crew was killed, the repair cost includes a 5/6 pilot or crew.
Armor repairs have no C-bill cost.
If a unit is abandoned without being \emph{destroyed}, commanders may repair the abandoned unit if they control the map at the end of the scenario.
Otherwise the unit is considered \emph{destroyed}.

\item {\bfseries Recruit}: Pay 50\% of the C-bill cost, rounded up, recruit new troops to replace troops in an infantry or Battle Armor unit that has not been \emph{destroyed}.
For example, if 1 out of 4 troops was killed in a Battle Armor squad, pay 50\% of the C-bill cost for 1 troop.
To recruit 1 troop in a squad of 4 IS Standard Battle Armor with Lasers, pay 293,125 C-bills.
Damage to Battle Armor troops that survive a scenario is repaired for free.
Use the \emph{Repair} rules for Battle Armor and infantry units damaged in an Alpha Strike scenario.

\item {\bfseries Refit}: Pay the difference in C-bill cost to refit a unit to a different variant.
A Phoenix Hawk PXH-2 costs 4,348,840 C-bills and a Phoenix Hawk PXH-1K costs 3,628,553.
A commander may pay 720,287 C-bills to convert a PHX-2 into a PHX-1K or to convert a PHX-1K into a PHX-2.
Note that it still costs C-bills to refit when the new variant is cheaper.
Refitting has a minimum cost of 250,000 C-bills or 10\% of the original C-bill cost of the unit, whichever is less.

\item {\bfseries Omni Refit}: OmniMechs can be temporarily configured as a cheaper variant for a scenario at no cost, but refitting is required to use more expensive variants.
For example, the Carrion Crow C is worth 10,336,492 C-bills.
The Carrion Crow A only costs 9,704,829 C-bills, so a Carrion Crow C can be temporarily configured as a Carrion Crow A for a scenario.
A Carrion Crow B costs 15,617,992 C-bills, so a Carrion Crow C would need a 5,281,500 C-bill refit to be converted to the Carrion Crow B variant.
Once the Carrion Crow C is refitted to a Carrion Crow B, the OmniMech can be configured as a Carrion Crow A, B, or C for any scenario.

\item {\bfseries Purchase}: Pay the C-bill cost to get a new unit.
Commanders must purchase units from their \href{http://www.masterunitlist.info}{Master Unit List} faction and era list.
The new unit has a pilot/crew at skill 4/5 and can be trained.

\item {\bfseries Salvage}: Pay 50\% the C-bill cost, rounded up, to salvage enemy units that that were destroyed in a scenario.
A War Crow Prime costs 22,057,358 C-bills, and a salvaged War Crow Prime costs 11,028,679 C-bills.
Salvage is the primary way to get units from a different \href{http://www.masterunitlist.info}{Master Unit List} faction list.
The new unit starts at skill 4/5 and can be trained.
Alternatively, commanders can earn 25\% of the C-bill cost by selling a salvaged unit.
A salvaged War Crow Prime could be sold to earn 5,514,340 C-bills instead of paying 11,028,679 C-bills to repair it.

\item {\bfseries Sell}: Commanders can sell units for 50\% of the C-bill cost or destroyed units for 25\% of the C-bill cost, rounded up.
A Locust LCT-1E costs 1,574,200 C-bills and can be sold for 787,100 C-bills.
If the Locust LCT-1E was destroyed, then selling it would only yield 393,550 C-bills.

\end{itemize}
