\item {\bfseries Retrain}: Retrain a pilot/crew to a new unit.
Commanders may retrain a pilot/crew when selling a unit and immediately purchasing a replacement unit of the same type or when exchanging the pilots/crew between two units.

Pay 250,000 C-bills multiplied by the difference in BV skill multiplier between their current skill level and 4/5 to retrain the crew/pilot.
For example, a 3/3 pilot has a BV skill multiplier of 1.44, so it costs 110,000 C-bills to retrain a 3/3 pilot for a new unit.
See \emph{BattleTech: TechManual}, page 315, for the BV skill multiplier table.
Add 250,000 C-bills to the retraining cost for pilots/crew with an SPA.
Each pilot/crew has to be retrained when exchanging the pilots/crew between two units.

The old and new unit must be the same type.
For example, a 'Mech pilot can only be retrained into another 'Mech unit.
A Combat Vehicle crew can only retrain to the same type of Combat Vehicle: ground, VTOL, WiGE, or naval.
See \emph{BattleTech: Total Warfare}, page 192, for discussion of the Combat Vehicle types.

\item {\bfseries Advanced Refit}: Pay double the difference in C-bill cost to refit a unit to a different variant that is only available on a different faction list.
The unit must be available in the current era.
A Locust LCT-1V is a common, widely available variant that costs 1,512,400 C-bills while the Locust LCT-6M costs 4,277,500 C-bills is only available to the Free Worlds League and the Word of Blake during the Civil War era.
A commander outside of the Free Worlds League or Word of Blake may pay 5,530,200 C-bills to convert a LCT-1V to a LCT-6M.
Converting back to a variant on the faction list only costs the standard \emph{Refit} cost.
Advanced refitting has a minimum cost of 500,000 C-bills or 20\% of the original C-bill cost of the unit, whichever is less.

\emph{Advanced Refit} can also be used to convert a unit a unique or experimental variant, if the force does not already contain a unique or experimental unit.
See \ifthenelse{\equal{\outworldsMode}{mode-pdf}}{page \pageref{subsec:force_construction}}{the \hyperref[subsec:force_construction]{Force Construction} rules} for restrictions on the single unique or experimental unit in a force.

There is not cost when using \emph{Advanced Refit} to permanently reduce the size of a Battle Armor or infantry unit, such as reducing a salvaged Elemental point with 5 troops to an Inner Sphere squad size of 4 troops.
Increasing the size of a Battle Armor or infantry unit would still incur the double cost penalty if the unit is from a different faction list; for example refitting a salvaged Gray Death Scout Suit squad with 4 troops to a 5 troop point would cost 1,040,160 C-bills for a faction that does not have the Gray Death Scout Suit on their faction list.

\item {\bfseries Advanced Omni Refit:} An \emph{Omni Refit} allows units to be temporarily converted to a cheaper variant for a scenario at no cost.
This variant must be available in the current era but does not need to be on the force's faction list.
Refitting is required to use more expensive variants.
As with the \emph{Advanced Refit}, pay double the difference in C-bill cost to refit a unit to a more expensive variant that is available on a different faction list.
Once the unit has been converted, it can be temporarily configured as a cheaper variant for a scenario at no cost.

\item {\bfseries Capture}: Capture a pilot or crew when their unit is destroyed.
A pilot or crew may eject from their 'Mech or abandon their vehicle.
See \emph{BattleTech: Tactical Operations Advanced Rules}, page 164, for rules on ejection and abandoning units.
This pilot or crew may be recovered by a friendly unit or captured by an enemy unit.
A captured pilot or crew may be ransomed, with terms agreed upon between the two commanders.
Alternatively, a captured pilot or crew may be taken as a bondsman and \emph{retrained} as above.

\item {\bfseries Allegiance}: Declare allegiance for to a single employer, such as a Great House, Clan, or wealthy benefactor.
The force receives logistical support in exchange for a portion each mission's objective payments.
Commanders must complete 5 scenarios before they can renounce their \emph{Allegiance}.

\begin{itemize}

\item Receive only 80\% of the payments for objectives

\item Always receive base pay, unless an objective awarded equipment

\end{itemize}

\pagebreak

\item {\bfseries Design Quirks}: Commanders may opt into using \emph{Design Quirks} for their entire force.
If a commander opts into using \emph{Design Quirks}, then they always apply to repair, replacement, salvage, and selling costs for all units.
Both sides must agree to use \emph{Design Quirks} for them to apply in a scenario.

See \emph{BattleTech: BattleMech Manual}, page 82, \emph{BattleTech: Campaign Operations}, page 225, or \href{https://sarna.net}{Sarna.net} for a list of all quirks.
See \href{https://megamek.org}{MegaMekLab} or \href{https://sarna.net}{Sarna.net} to determine which quirks apply to units.

Some quirks require modifications to fit in the Outworlds Wastes rules.

\begin{itemize}

\item Two 'Mechs with \emph{Compact 'Mech} may share a dropship bay.

\item \emph{Easy to Maintain} reduces repair and replacement costs by 10\%.

\item \emph{Good Reputation} increases purchase and salvage costs by 10\%.

\item \emph{Modular Weapons} decreases refit costs by 50\%.

\item \emph{Rugged} has no effect.

\item \emph{Ubiquitous} reduces repair and replacement costs by 10\%.

\item \emph{Bad Reputation} decreases purchase and salvage costs by 10\%.

\item \emph{Difficult to Maintain} increases repair and replacement costs by 10\%.

\item \emph{Non-Standard Parts} increases repair and replacement costs by 10\%.

\end{itemize}

\item {\bfseries Custom Design Quirks}: If commanders have opted into using \emph{Design Quirks}, they may purchase additional quirks to customize their units.
If a commander opts into using \emph{Custom Design Quirks}, then they always apply to repair, replacement, salvage, and selling costs for all units.
Both sides must agree to use \emph{Custom Design Quirks} for them to apply in a scenario.

Pay 10\% of the unit's cost in C-bills per positive quirk point to add a positive quirk.
For each positive quirk, commanders must select negative quirks with a total value equal or higher than the positive quirk's point value.
Increase the repair and replacement costs by 10\% for each positive quirk point purchased.
See \emph{BattleTech: Campaign Operations}, page 255, for a table summarizing which quirks may be applied to which unit types.

The following quirks may be used to customize your units:
