Commanders may create an Event Play detachment with units from an existing League Play force.
This detachment must follow the restrictions given in the \ifthenelse{\equal{\outworldsMode}{mode-web}}{\hyperref[subsec:force_construction_scale_1]{Event Play Force Construction}}{\emph{Event Play Force Construction}} rules\ifthenelse{\equal{\outworldsMode}{mode-web}}{}{ (see p. \pageref{subsec:force_construction_scale_1})}.
These units use their current skills and SPAs from the League Play force.

Commanders must send a Warchest of at least 1,000 SP but no more than 3,000 SP with the detachment.
In order to return to the League Play force, the Event Play detachment has to pay 300 SP in transportation costs, modified by contract terms, after the event to return to the location of the League Play force.
Add any additional SP earned by the Event Play detachment to the League Play force's Warchest.

An Event Play force may also be used to make a new League Play force.
After the event, commanders must use all of the units in the Event Play force and add additional units per the restrictions given in the \ifthenelse{\equal{\outworldsMode}{mode-web}}{\hyperref[subsec:force_construction_scale_2]{League Play Force Construction}}{\emph{League Play Force Construction}} rules\ifthenelse{\equal{\outworldsMode}{mode-web}}{}{ (see p. \pageref{subsec:force_construction_scale_2})}.
Units in this new League Play force may retain any Skill Advances earned during Event Play.
Also, if the Event Play force has more than 3,000 SP in the Warchest, then the new League Play force starts with this Warchest.
Otherwise, the new League Play force starts with a Warchest of 3,000 SP.
